\documentclass[11pt,a4paper]{altacv}

\geometry{left=1cm,right=1cm,top=1.5cm,bottom=1cm,columnsep=0.8cm}

\usepackage{paracol}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}

\usepackage{hyperref}
\AtBeginDocument{%
  \hypersetup{%
    hidelinks,
    colorlinks=false,
    pdfborder={0 0 0},
    pdfhighlight=/N
  }%
}
\urlstyle{same}

\definecolor{Teal}{HTML}{008080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Teal}
\colorlet{accent}{Teal}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\linespread{0.95}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\AtBeginEnvironment{itemize}{%
  \small
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
}

\renewcommand{\namefont}{\LARGE\bfseries}
\renewcommand{\taglinefont}{\normalsize\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\makeatletter
\renewcommand{\makecvheader}{%
  \begingroup
    \begin{minipage}{\linewidth}%
    \raggedright%
    {\namefont\color{name}\MakeUppercase{\@name}\par}
    \smallskip
    {\taglinefont\color{tagline}\@tagline\par}
    \smallskip
    {\personalinfofont\@personalinfo\par}
    \end{minipage}\par%
  \endgroup
}
\makeatother

\begin{document}

\name{Mustafa Arinmiş}
\tagline{Backend Software Engineer}

\personalinfo{%
    \email{mustafa\_arinmis@outlook.com}
    \phone{+90 543 549 99 53}
    \location{Antalya, Turkiye}
    \github{\href[pdfnewwindow=true]{https://github.com/arinmis}{github.com/arinmis}}
    \linkedin{\href[pdfnewwindow=true]{https://www.linkedin.com/in/arinmis}{linkedin.com/in/arinmis}}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\columnratio{1}
\begin{paracol}{1}

\cvsection{Profile}
Backend-focused \textbf{Software Engineer} building \textbf{scalable APIs} and \textbf{event-driven microservices} in \textbf{.NET}. Experienced with cloud-native \textbf{AWS} deployments using \textbf{Docker}, \textbf{Kubernetes}, and \textbf{CI/CD}. Focused on reliability and shipping production-grade systems.

\cvsection{Experience}

\cvevent{Backend Software Engineer}{\href{https://www.octopusplus.com}{SAN TSG}}{Dec 2024 -- Present}{Antalya, Turkiye}
\begin{itemize}
  \item Engineered and deployed \textbf{5 production .NET 10 microservices} end-to-end (API, schema, tests, observability, infra) in a 30+ service tourism platform (excursion, flight, hotel booking) using \textbf{Clean/Onion architecture}, \textbf{CQRS} (MediatR), \textbf{FluentValidation}.
  \item Implemented the \textbf{Dapr} sidecar for microservice communication, abstracting distributed-system patterns (pub/sub) over \textbf{RabbitMQ} with polyglot persistence (\textbf{EF Core + PostgreSQL}, \textbf{MongoDB}, \textbf{Redis} for state management).
  \item Enabled scalable deployments with \textbf{Docker} and \textbf{Kubernetes} on \textbf{AWS EKS} via GitOps (\textbf{Bitbucket} $\rightarrow$ CodeBuild $\rightarrow$ ECR $\rightarrow$ \textbf{Kustomize} $\rightarrow$ \textbf{ArgoCD}); observability via \textbf{OpenTelemetry} + \textbf{Grafana}/\textbf{Loki}/\textbf{Tempo}, behind \textbf{Kong Gateway}.
  \item Engineered and led the \textbf{core MCP (Model Context Protocol) server} for \textbf{30+ .NET microservices}, exposing intent-shaped tools that reuse existing contracts and \textbf{JWT auth}, and architected an \textbf{LLM-independent AI Agent Service} (\textbf{Python LangChain} + \textbf{LangSmith}) with runtime tool discovery; built a \textbf{Python/Flask RAG service} applying advanced NLP over technical documentation and APIs (\textbf{ChromaDB}; \href{https://docs-ai.santsg.com}{\textbf{docs-ai.santsg.com}}). Mentored 2 interns and hired a CS student to a part-time engineer role.
  \item Created an automated \textbf{Python} service to collect employee utilization metrics from \textbf{Bitbucket}, \textbf{JIRA}, and worklogs, which includes email automation and is deployed to \textbf{AWS ECR}.
\end{itemize}

\divider

\cvevent{Backend Software Engineer (Contract)}{Mavi ArGe}{Oct 2024 -- Dec 2024}{Antalya, Turkiye}
\begin{itemize}
  \item Developed \textbf{.NET} REST APIs for an EV charging station Fleet Management \textbf{IoT} system (\textbf{TÜBİTAK} project), including a rule-based engine for battery telemetry and monitoring dashboards.
\end{itemize}

\divider

\cvevent{Full Stack Software Developer}{\href{https://piworks.net/products}{P.I. Works}}{Jun 2023 -- Sep 2024}{Remote, Istanbul, Turkiye}
\begin{itemize}
  \item Developed new features, increased unit test coverage, and refactored code smells for an \textbf{Angular-.NET} enterprise telco platform.
\end{itemize}

\divider

\cvevent{Frontend Developer}{\href{https://linarit.com/img/pqm-flyer.pdf}{Linarit}}{Feb 2022 -- Sep 2022}{Antalya, Turkiye}
\begin{itemize}
  \item Developed key features for the \textbf{React}-based \textbf{Linarit PQM Industrial IoT platform}, including real-time \textbf{gRPC} data visualization, client-side caching, and performance optimizations.
\end{itemize}

\divider

\cvevent{Founder Software Developer}{AudioHealer}{Sep 2021 -- Feb 2022}{Antalya, Turkiye}
\begin{itemize}
  \item Built \href{https://www.audiohealer.com}{AudioHealer}, a full-stack AI-powered audio enhancement platform: \textbf{DTLN} (TensorFlow/Keras) neural network for real-time noise suppression, \textbf{FFmpeg} 18-band EQ and EBU R128 loudness normalization pipeline, \textbf{Flask} backend on \textbf{Google Cloud Run}, \textbf{Svelte} web frontend, and \textbf{Flutter} mobile client. Applied to Y Combinator.
\end{itemize}

\cvsection{Skills}
{\small\vspace{2pt}
\begin{tabular}{p{0.18\linewidth} p{0.8\linewidth}}
\textbf{Languages}      & Python, C\#, JavaScript/TypeScript \\
\textbf{Frameworks}     & .NET, Flask, Angular, React, Node.js \\
\textbf{AI / LLM}        & LangChain, LangGraph, llama-cpp, ChromaDB, FastAPI \\
\textbf{Cloud \& DevOps} & AWS (ECR, EKS, ECS, Lambda, S3), Docker, Kubernetes, Helm, CI/CD \\
\textbf{Data}           & RabbitMQ, Redis, PostgreSQL, MongoDB \\
\textbf{Architecture}   & REST APIs, Event-Driven Microservices, Dapr, gRPC, CQRS, Clean Architecture, Multi-Tenant \\
\textbf{Tools}          & Git, Linux, Vim, Tmux, Claude Code, VS Code \\
\end{tabular}\smallskip
}

\cvsection{Projects}
\textbf{Nand2Tetris} — \href{https://github.com/arinmis/nand2tetris}{github.com/arinmis/nand2tetris} \\
HDL, Python, Assembly — A full computer system implementation from boolean gates to a high-level language.

\textbf{Tiro} — \href{https://tiro.legal}{tiro.legal} \\
Python, FastAPI, Electron, React, SQLite, ChromaDB, llama-cpp — Desktop app for lawyers to manage case files with built-in local LLM (RAG) for document analysis. Cross-platform executable. Built with a part-time collaborator.

\textbf{o-pt-pt} — \href{https://o-pt-pt.com}{o-pt-pt.com} \\
Next.js, React, Tamagui, Prisma, PostgreSQL — Multi-tenant SaaS for personal trainers to manage customers, workout plans, exercises, and progress tracking. Cross-platform UI (web + native) via Tamagui.

\cvsection{Education}
\textbf{B.Sc. Computer Engineering}, Akdeniz University, Antalya \hfill 2019 -- 2024

\end{paracol}
\end{document}
