\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
\setmainfont{XCharter}[
  UprightFont = *-Roman,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
  Ligatures = TeX,
]
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{multicol}

\definecolor{accent}{HTML}{1A2733}
\definecolor{subtle}{HTML}{666666}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{2.0in}

\urlstyle{rm}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{%
  \normalfont\large\bfseries\color{accent}%
}{}{0em}{}[{\color{subtle}\vspace{1pt}\titlerule[0.4pt]}]
\titlespacing*{\section}{0pt}{6pt}{2pt}

\newcommand{\resumeSubheading}[4]{%
  \vspace{2pt}%
  \noindent{\bfseries #1}\hfill {\small #4}\par%
  \noindent{\itshape\color{subtle} #3 \,$\cdot$\, #2}\par%
  \vspace{1pt}%
}

\newcommand{\resumeProject}[3]{%
  \vspace{2pt}%
  \noindent{\bfseries #1}\hfill {\small #3}\par%
  \noindent{\itshape\color{subtle} #2}\par%
  \vspace{1pt}%
}

\setlist[description]{leftmargin=14pt, itemsep=1pt, topsep=1pt, parsep=0pt}
\setlist[itemize]{leftmargin=14pt, label=\textbullet, itemsep=0pt, topsep=0pt, parsep=0pt}

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\fontsize{22pt}{26pt}\selectfont\bfseries\color{accent} Mustafa Arinmis}\\[4pt]
  {\small\color{subtle} mustafa\_arinmis@outlook.com \, $\bullet$ \, +90 543 549 99 53 \, $\bullet$ \, \href{https://github.com/arinmis}{github.com/arinmis} \, $\bullet$ \, \href{https://www.linkedin.com/in/arinmis}{linkedin.com/in/arinmis}}\\[2pt]
  {\small\color{subtle} Antalya, Turkiye \,$\cdot$\, BSc Computer Engineering, Akdeniz University}
\end{center}
\vspace{1pt}

%-----------SUMMARY-----------------
\section{Summary}
\textbf{Full-Stack Software Engineer} building end-to-end solutions across \textbf{.NET}, \textbf{Python}, \textbf{React}/\textbf{Angular}. Designed and deployed \textbf{5 production microservices} in a 30-service tourism platform (\textbf{.NET 10}, \textbf{CQRS}, \textbf{Dapr}, \textbf{AWS EKS}). Experienced with event-driven architecture, \textbf{AWS}, and \textbf{Docker}/\textbf{Kubernetes}.


%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubheading{SAN TSG (OctopusPlus)}{Antalya, Turkiye}{Full Stack Software Engineer}{Dec 2024 -- Present}
\begin{itemize}
  \item Designed, built, and deployed \textbf{5 production microservices} in a 30-service tourism platform --- \textbf{.NET 10}, \textbf{CQRS}, \textbf{Dapr} pub/sub over \textbf{RabbitMQ}; polyglot persistence (\textbf{EF Core + PostgreSQL}, \textbf{MongoDB}, \textbf{Redis}); deployed to \textbf{AWS EKS} via GitOps (\textbf{ArgoCD}), behind \textbf{Kong Gateway}.
  \item Mentored 2 interns and hired a CS student to a part-time engineer role.
  \item Built a production \textbf{MCP (Model Context Protocol)} AI infrastructure for \textbf{25+ .NET microservices}: a \textbf{.NET 10 MCP server} exposing intent-shaped tools that reuse existing contracts and JWT auth, fronted by a \textbf{Python LangChain agent} (GPT-4.1) with runtime tool discovery (\href{https://docs-ai.santsg.com}{\textbf{docs-ai.santsg.com}} RAG service, \textbf{ChromaDB}, \textbf{Python/Flask}; built a \textbf{Bitbucket}/\textbf{JIRA} metrics service).
\end{itemize}

\resumeSubheading{Mavi ArGe}{Antalya, Turkiye}{Full Stack Software Engineer (Contract)}{Oct 2024 -- Dec 2024}
\begin{itemize}
  \item Built a \textbf{full-stack} EV charging Fleet Management \textbf{IoT} system (\textbf{TÜBİTAK} project): \textbf{.NET} REST APIs, a rule-based engine processing battery telemetry, and monitoring dashboards with real-time owner notifications.
\end{itemize}

\resumeSubheading{P.I. Works}{Remote, Istanbul, Turkiye}{Full Stack Software Developer}{Jun 2023 -- Sep 2024}
\begin{itemize}
  \item Developed new features, increased unit test coverage, and refactored code smells for an \textbf{Angular-.NET} enterprise telco platform serving thousands of network devices.
\end{itemize}

\resumeSubheading{AudioHealer}{Antalya, Turkiye}{Founder Software Developer}{Sep 2021 -- Feb 2022}
\begin{itemize}
  \item Built \href{https://www.audiohealer.com}{AudioHealer}, a full-stack AI audio platform: \textbf{DTLN} neural network for noise suppression, \textbf{FFmpeg} EQ/loudness pipeline, \textbf{Flask} backend on \textbf{Google Cloud Run}, \textbf{Svelte} web + \textbf{Flutter} mobile, \textbf{Firebase} Auth/\textbf{Firestore}, freemium with \textbf{iyzico} payments, multi-language.
  \item Applied to Y Combinator.
\end{itemize}

\resumeSubheading{Linarit}{Antalya, Turkiye}{Full Stack Developer}{Feb 2022 -- Sep 2022}
\begin{itemize}
  \item Developed both frontend and backend integrations for the Linarit PQM Industrial IoT platform: \textbf{React} UI with real-time \textbf{gRPC} data visualization, interfacing with a \textbf{5-service microservices} architecture and IoT edge devices.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\resumeProject{B.Sc. Computer Engineering}{Akdeniz University, Antalya}{2019 -- 2024}

%-----------PROJECTS-----------------
\section{Projects}
\resumeProject{Tiro}{\href{https://tiro.legal}{tiro.legal}}{}
\begin{itemize}
  \item Desktop legal case manager with built-in local LLM (RAG) for lawyers. \textbf{Python}, \textbf{FastAPI}, \textbf{Electron}, \textbf{React}, \textbf{SQLite}, \textbf{ChromaDB}. Cross-platform executable via \textbf{PyInstaller}.
\end{itemize}

\resumeProject{FitBrand}{\href{https://fitbrand.app}{fitbrand.app}}{}
\begin{itemize}
  \item White-label PWA for personal trainers — each trainer gets a fully branded app with custom logo, colors, app icon, and domain. AI-powered workout plans, client management, progress tracking, messaging, and a built-in blog. Installs to the home screen as a \textbf{PWA} (no App Store). \textbf{Next.js}, \textbf{React}, \textbf{Tamagui}, \textbf{Prisma}, \textbf{PostgreSQL}. \textbf{MCP} tools for AI features.
\end{itemize}

\end{document}
