\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
\setmainfont{XCharter}[
  UprightFont = *-Roman,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
  Ligatures = TeX,
]
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{multicol}

\definecolor{accent}{HTML}{1A2733}
\definecolor{subtle}{HTML}{666666}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{2.0in}

\urlstyle{rm}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{%
  \normalfont\large\bfseries\color{accent}%
}{}{0em}{}[{\color{subtle}\vspace{1pt}\titlerule[0.4pt]}]
\titlespacing*{\section}{0pt}{6pt}{2pt}

\newcommand{\resumeSubheading}[4]{%
  \vspace{2pt}%
  \noindent{\bfseries #1}\hfill {\small #4}\par%
  \noindent{\itshape\color{subtle} #3 \,$\cdot$\, #2}\par%
  \vspace{1pt}%
}

\newcommand{\resumeProject}[3]{%
  \vspace{2pt}%
  \noindent{\bfseries #1}\hfill {\small #3}\par%
  \noindent{\itshape\color{subtle} #2}\par%
  \vspace{1pt}%
}

\setlist[description]{leftmargin=14pt, itemsep=1pt, topsep=1pt, parsep=0pt}
\setlist[itemize]{leftmargin=14pt, label=\textbullet, itemsep=0pt, topsep=0pt, parsep=0pt}

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\fontsize{22pt}{26pt}\selectfont\bfseries\color{accent} Mustafa Arinmis}\\[4pt]
  {\small\color{subtle} mustafa\_arinmis@outlook.com \, $\bullet$ \, +90 543 549 99 53 \, $\bullet$ \, \href{https://github.com/arinmis}{github.com/arinmis} \, $\bullet$ \, \href{https://www.linkedin.com/in/arinmis}{linkedin.com/in/arinmis}}\\[2pt]
  {\small\color{subtle} Antalya, Turkiye \,$\cdot$\, BSc Computer Engineering, Akdeniz University}
\end{center}
\vspace{1pt}

%-----------SUMMARY-----------------
\section{Summary}
Backend-focused \textbf{Software Engineer} with an \textbf{E2E product ownership mindset}. Designed and deployed \textbf{5 production microservices} in a 30+ service tourism platform (\textbf{.NET 10}, \textbf{CQRS}, \textbf{Dapr}, \textbf{AWS EKS}). Experienced with APIs, event-driven architecture, and cloud-native deployments.


%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubheading{SAN TSG (OctopusPlus)}{Antalya, Turkiye}{Backend Software Engineer}{Dec 2024 -- Present}
\begin{itemize}
  \item Engineered and deployed \textbf{5 production .NET 10 microservices} end-to-end (API, schema, tests, observability, infra) in a 30+ service tourism platform (excursion, flight, hotel booking) using \textbf{Clean/Onion architecture}, \textbf{CQRS} (MediatR), \textbf{FluentValidation}.
  \item Implemented the \textbf{Dapr} sidecar for microservice communication, abstracting distributed-system patterns (pub/sub) over \textbf{RabbitMQ} with polyglot persistence (\textbf{EF Core + PostgreSQL}, \textbf{MongoDB}, \textbf{Redis} for state management).
  \item Enabled scalable deployments with \textbf{Docker} and \textbf{Kubernetes} on \textbf{AWS EKS} via GitOps (\textbf{ArgoCD}); observability via \textbf{OpenTelemetry} + \textbf{Grafana}/\textbf{Loki}/\textbf{Tempo}, behind \textbf{Kong Gateway}.
  \item Engineered and led the \textbf{core MCP (Model Context Protocol) server} for \textbf{30+ .NET microservices}, exposing intent-shaped tools that reuse existing contracts and \textbf{JWT auth}, and architected an \textbf{LLM-independent AI Agent Service} (\textbf{Python LangChain} + \textbf{LangSmith}) with runtime tool discovery; built a \textbf{Python/Flask RAG service} applying advanced NLP over technical documentation and APIs (\textbf{ChromaDB}; \href{https://docs-ai.santsg.com}{\textbf{docs-ai.santsg.com}}). Mentored 2 interns and hired a CS student to a part-time engineer role.
  \item Created an automated \textbf{Python} service to collect employee utilization metrics from \textbf{Bitbucket}, \textbf{JIRA}, and worklogs, which includes email automation and is deployed to \textbf{AWS ECR}.
\end{itemize}

\resumeSubheading{Mavi ArGe}{Antalya, Turkiye}{Backend Software Engineer (Contract)}{Oct 2024 -- Dec 2024}
\begin{itemize}
  \item Developed \textbf{.NET} REST APIs for an Electric Vehicle charging station Fleet Management \textbf{IoT} system (\textbf{TÜBİTAK} project), including a rule-based engine for battery telemetry and monitoring dashboards.
\end{itemize}

\resumeSubheading{P.I. Works}{Remote, Istanbul, Turkiye}{Full Stack Software Developer}{Jun 2023 -- Sep 2024}
\begin{itemize}
  \item Developed new features, increased unit test coverage, and refactored code smells for an \textbf{Angular-.NET} enterprise telco platform.
\end{itemize}

\resumeSubheading{Linarit}{Antalya, Turkiye}{Frontend Developer}{Feb 2022 -- Sep 2022}
\begin{itemize}
  \item Developed key features for the \textbf{React}-based \textbf{Linarit PQM Industrial IoT platform}, including real-time \textbf{gRPC} data visualization, client-side caching, and performance optimizations.
\end{itemize}

\resumeSubheading{AudioHealer}{Antalya, Turkiye}{Founder Software Developer}{Sep 2021 -- Feb 2022}
\begin{itemize}
  \item Built \href{https://www.audiohealer.com}{AudioHealer}, a full-stack AI-powered audio enhancement platform: \textbf{DTLN} (TensorFlow/Keras) neural network for real-time noise suppression, \textbf{FFmpeg} 18-band EQ and EBU R128 loudness normalization pipeline, \textbf{Flask} backend on \textbf{Google Cloud Run}, \textbf{Svelte} web frontend, and \textbf{Flutter} mobile client. Applied to Y Combinator.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\resumeProject{B.Sc. Computer Engineering}{Akdeniz University, Antalya}{2019 -- 2024}

%-----------PROJECTS-----------------
\section{Projects}
\resumeProject{Tiro}{\href{https://tiro.legal}{tiro.legal}}{}
\begin{itemize}
  \item Desktop legal case manager with built-in local LLM (RAG) for lawyers. \textbf{Python}, \textbf{FastAPI}, \textbf{Electron}, \textbf{React}, \textbf{SQLite}, \textbf{ChromaDB}. Cross-platform executable.
\end{itemize}

\resumeProject{FitBrand}{\href{https://fitbrand.app}{fitbrand.app}}{}
\begin{itemize}
  \item White-label PWA for personal trainers — fully branded apps with custom logo, colors, domain. AI workout plans, client management, messaging, blog. Installs as \textbf{PWA} (no App Store). \textbf{Next.js}, \textbf{Tamagui}, \textbf{Prisma}, \textbf{PostgreSQL}. \textbf{MCP} tools for AI.
\end{itemize}

\end{document}
